Lessons Learned about JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2020-01-20 ms.tex
updated dynamic spectrum w/ colorbrand F322W2 flat

\begin{figure*}
%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
\gridline{\fig{o9LEDwFlat_dyn_spec_NRCN83-256-O9LW.pdf}{0.55\textwidth}{Dynamic Spectrum}
\fig{o9LEDwFlat_bb_series_NRCN83-256-O9LW.pdf}{0.44\textwidth}{Broadband Time Series}}
%\gridline{\fig{o9LEDwFlat_ind_spec_NRCN83-256-O9LW.pdf}{0.44\textwidth}{Representative Spectrum}
%}
\caption{The dynamic spectrum of the grism along shows large artifacts due to motion of the source (broad horizontal stripes), that also show up in the integrated broadband time series.
The effect of image motion along the dispersion direction is visible as broad stripes
}\label{fig:otisLWdynSpec}
\end{figure*}

>>>>

\begin{figure*}
%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
\gridline{\fig{o9LEDwf322w2Flat_dyn_spec_NRCN83-256-O9LW}{0.58\textwidth}{Dynamic Spectrum}
\fig{o9LEDwFlat_bb_series_NRCN83-256-O9LW.pdf}{0.41\textwidth}{Broadband Time Series}}
%\gridline{\fig{o9LEDwFlat_ind_spec_NRCN83-256-O9LW.pdf}{0.44\textwidth}{Representative Spectrum}
%}
\caption{The dynamic spectrum of the grism along shows large artifacts due to motion of the source (broad horizontal stripes), that also show up in the integrated broadband time series.
The effect of image motion along the dispersion direction is visible as broad stripes
}\label{fig:otisLWdynSpec}
\end{figure*}
